Formal Solutions To ODE's

### 2015-11-16 cheatsheets/ode_formal_slns.tex
Added nonhomogeneous solutions

>>>>

\section{Nonhomogeneous}

Suppose we have the following differential equation.
\begin{equation}\label{eqn2}
	ay'' + by' +cy = f(x)
\end{equation}

We begin by finding the solution to the homogeneous equation,
\[
	ay'' + by' +cy = 0.
\]
Call this solution the general solution or $y_g$.
Note, do \textbf{NOT} apply any initial conditions for this solution.

We now have a table for $f(x)$ and the form of the particular solution.
\[
\begin{array}{|c|c|}
\hline
f & y_p\\\hline
x & Ax+B\\\hline
x^2 & Ax+B+C\\\hline
e^x & Ae^x\\\hline
\cos(n\pi x) \text{ or } \sin(n\pi x) & A\cos(n\pi x) + B\sin(n\pi x)\\\hline
x\cos(n\pi x) \text{ or } \sin(n\pi x) & (Ax+B)\cos(n\pi x) + (Cx +D)\sin(n\pi x)\\\hline
\end{array}
\]
To find the $A,B,C,D$, plug $y_p$ back into \autoref{eqn2}, and match terms with $f(x)$.
The solution to \autoref{eqn2} is $y=y_g+y_p$.
Now apply your initial conditions to determine your as of now undetermined coefficients.
